---
title: "Lending Club Dashboard"
date: '`r format(Sys.time(),"%B %d, %Y %H:%m")`'
output: html_document
params:
  investorID: NA 
  APIkey: NA

---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
library(LendingClub)
suppressPackageStartupMessages(library(dplyr))
library(knitr)
suppressMessages(library(ggplot2))


LC_CRED<- lc_MakeCredential(params$investorID, params$APIkey)
holdings<- LendingClub::lc_DetailedNotesOwned()$content

summarydata<-  lc_AccountSummary()$content

atRisk<- {
  at_risk_status<- c("Late (16-30 days)",
                     "Late (31-120 days)",
                     "Charged Off")
  x<- holdings[holdings$loanStatus %in% at_risk_status,]    
  sum(as.numeric(x$noteAmount)- as.numeric(x$principalReceived))
  }
```

### Account KPIs  

```{r summaryTable}

stats<- c("Account Total",
          "Available Cash",
          "Interest Received",
          "Principal at Risk",
          "Interest-Risk (IR) Ratio")

vals<- as.numeric(c(summarydata$accountTotal,
                    summarydata$availableCash,
                    summarydata$receivedInterest,
                    atRisk,
                    round(as.numeric(summarydata$receivedInterest)/atRisk,2)))

summtable<- data.frame(stats, vals)

kable(summtable, 
      col.names= NULL,
      align = c("l","r"), 
      format.args = list(big.mark = ','),
      padding = 2) 
```


  

### Portfolio Summary  

```{r matrix}


x<-lapply(split(holdings, f= holdings$portfolioName), summary)
x<- c(x, list( summary (holdings)))
names(x)[length(x)]<- "Total"

for (i in 1:length(x)){
  names(x[[i]])[2] <- names(x[i])
  }


y<- Reduce(function(...) merge(..., by= 'col_labs',  all.x=TRUE), x)
y<- y[c(1,4,3,8,6,5,7,9,2), ]
colnames(y)[1]<- ""
kable(y,
  row.names= FALSE,
  format.args = list(big.mark = ','),
  padding = 2) 
```

### Principal Distribution by Grade 

```{r, fig.align='center', fig.height=3}

h<- ggplot(holdings %>% 
               filter(currentPaymentStatus != "ChargedOff") %>%
               mutate(majGrade = strtrim(grade, 1)) %>%
               group_by(majGrade) %>% 
               summarize(total = round(sum(as.numeric(principalPending))),0))
h<- h + aes(x= majGrade, y= total, label=total)
h<- h + geom_col()
h<- h + theme_classic()
h<- h + labs(x= "Grade",
             y= "Outstanding Principal")
h<- h + geom_text(vjust=0, nudge_y=.7, size=3.5)
h
```

###Payback Ratio {.tabset}

#### Chart

```{r, fig.align='center'}
dat<-holdings %>%
  mutate(CFRatio= round((as.numeric(paymentsReceived) - as.numeric(noteAmount)) /as.numeric(noteAmount)*100,2)+100 +1,
         orderDate= as.Date(orderDate))

dat$simpleStatus <- case_when(dat$loanStatus == "Charged Off" ~ "Dead",
                              dat$loanStatus == "Current" ~"Performing",
                              dat$loanStatus == "Fully Paid" ~ "Complete",
                              dat$loanStatus == "In Grace Period" ~ "Performing",
                              dat$loanStatus == "In Review" ~ "Performing",
                              dat$loanStatus == "Issued" ~ "Performing",
                              dat$loanStatus == "Late (16-30 days)" ~ "Late",
                              dat$loanStatus == "Late (31-120 days)" ~ "Late")

ThreeYear<- as.Date(Sys.time())-(365*3)
FiveYear<- as.Date(Sys.time()-(365*5))

status_colors<-c("Performing"="#377eb8", #blue
                 "Late"= "#e41a1c", #red
                 "Dead"="#707070", #gray
                 "Complete"= "#4daf4a") #gree

g<- ggplot(dat)
g<- g + aes(x= as.Date(Sys.time())-orderDate, 
            y= CFRatio, 
            group= portfolioName,
            fill= simpleStatus)
g<- g + geom_point(aes(colour=simpleStatus), size=1)
g<- g + scale_colour_manual(values=status_colors)
g<- g + scale_x_continuous()
g<- g + facet_wrap(~portfolioName, ncol=2)
g<- g + theme_classic()
g<- g + labs(x= "Age in Days",
             y= "Payback Ratio")
g<- g + geom_hline(yintercept = 100, linetype="dashed")
g<- g + theme(legend.position="none",
              panel.border  = element_rect(colour = "black", fill=NA))
g
```

#### Late Notes

```{r}
LateNotes<- dat %>%
    filter(simpleStatus=="Late") %>%
    mutate(LastPayment= as.Date(lastPaymentDate),
           DaysLate=as.Date(Sys.time())- LastPayment) %>%
    select(portfolioName, grade, purpose, CFRatio, principalPending, LastPayment, DaysLate)


kable(LateNotes, 
      col.names= c("Portfolio",
                   "Grade",
                   "Purpose",
                   "Payback Ratio",
                   "Outstanding Principal",
                   "Last Payment",
                   "Days Since Payment"),
      align = c("l","l","l","r","r","l","l"), 
      format.args = list(big.mark = ','),
      padding = 2) 
```

## 

<hr>
**Principal At Risk** includes outstanding principal of notes greater than 16 days late and notes that have been charged off. 

**At Risk Ratio** is the Principal at Risk as a percentage of the note amount. This is a measure of portfolio health indicating how much of the invesmet is at risk for defaulting or has already done so. 

**Interest-Risk (IR) Ratio** is the ratio of interest payments received to the principal at risk in the portfolio

**Wgt Int Rate** interest rate weighted by the outstanding principal. 

**Payback Ratio** measures the difference between cash invested in a note and the total payments received. The payments include both interest and principal. All notes start at zero and will increase as payments are made.  A note with a ratio greater than 100 indicates that more cash was received than was initially invested. Notes will start at the bottom left of the chart and trend towards the upper right corner as they mature.   

#### [Lending Club](http://www.lendingclub.com)