---
title: "Lending Club Dashboard"
date: '`r format(Sys.time(),"%B %d, %Y")`'
output: html_document
params:
  investorID: NA 
  APIkey: NA

---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
library(LendingClub)
library(dplyr)
library(knitr)
library(tidyr)
suppressMessages(library(ggplot2))


LC_CRED<- MakeCredential(params$investorID, params$APIkey)
holdings<- LendingClub::DetailedNotesOwned()$content

summarydata<-  {
  x<- AccountSummary()$content
  y <- as.data.frame(t(x[,2]), stringsAsFactors = F)
  colnames(y)<- t(x[,1])
  y
  }

atRisk<- {
  at_risk_status<- c("Late (16-30 days)",
                     "Late (31-120 days)",
                     "Charged Off")
  x<- holdings[holdings$loanStatus %in% at_risk_status,]    
  sum(as.numeric(x$noteAmount)- as.numeric(x$principalReceived))
  }
```

### Account KPIs  

```{r summaryTable}

stats<- c("Account Total",
          "Available Cash",
          "Interest Received",
          "Principal at Risk",
          "Ratio")

vals<- as.numeric(c(summarydata$accountTotal,
                    summarydata$availableCash,
                    summarydata$receivedInterest,
                    atRisk,
                    round(as.numeric(summarydata$receivedInterest)/atRisk,2)))

summtable<- data.frame(stats, vals)

kable(summtable, 
      col.names= NULL,
      align = c("l","r"), 
      format.args = list(big.mark = ','),
      padding = 2) 
```

### Portfolio Summary  

```{r matrix}
portfolio_matrix<- function(x) {
  
  col_labs<- c(
    "Amount Invested",
    "Discount",
    "Charged Off",
    "Principal Received",
    "Net Outstanding",
    "Interest Received",
    "Payments Received",
    "Wgt Int Rate")
  
  order<- c(1:8)
  
  vals<- c( 
    sum(as.numeric(x$noteAmount)), # Amount Invested
    sum(as.numeric(x$principalReceived) + as.numeric(x$principalPending) - as.numeric(x$noteAmount)), # Discount
    -sum(ifelse(x$currentPaymentStatus=="ChargedOff", as.numeric(x$principalPending),0)), #Charged off
    -sum(as.numeric(x$principalReceived)),  # Principal received
    sum(ifelse(x$currentPaymentStatus=="ChargedOff",0, as.numeric(x$principalPending))), # net outstanding
    sum(as.numeric(x$interestReceived)), 
    sum(as.numeric(x$paymentsReceived)), 
    round( sum(as.numeric(x$interestRate) * as.numeric(x$principalPending)) / sum(as.numeric(x$principalPending)), 2)
  )
  
  data.frame(order, col_labs, vals)
  
  }


x<-lapply(split(holdings, f= holdings$portfolioName), portfolio_matrix)
x<- c(x, list(portfolio_matrix(holdings)))
names(x)[length(x)]<- "Total"

for (i in 1:length(x)){
  names(x[[i]])[3] <- names(x[i])
  }


y<- Reduce(function(...) merge(..., by=c('col_labs','order'),  all.x=TRUE), x)
colnames(y)[1]<- ""
y<- y[order(y$order),]
y$order<- NULL
kable(y,
  row.names= FALSE,
  format.args = list(big.mark = ','),
  padding = 2) 
```

### Distribution by Grade 

```{r}
h<- ggplot(holdings %>% group_by(grade) %>% summarize(counts =n()))
h<- h + aes(x= strtrim(grade, 1), y= counts)
h<- h + geom_bar(stat='identity')
h<- h + theme_classic()
h<- h + labs(x= "Grade",
             y= "Loan Count")
h

```

### Payback Ratio 

```{r, fig.align='center'}
dat<-holdings %>%
  mutate(CFRatio= round((as.numeric(paymentsReceived) - as.numeric(noteAmount)) /as.numeric(noteAmount)*100,2)+100 +1,
         orderDate= as.Date(orderDate))

dat$simpleStatus <- case_when(dat$loanStatus == "Charged Off" ~ "Complete",
                              dat$loanStatus == "Current" ~"Performing",
                              dat$loanStatus == "Fully Paid" ~ "Complete",
                              dat$loanStatus == "In Grace Period" ~ "Performing",
                              dat$loanStatus == "In Review" ~ "Performing",
                              dat$loanStatus == "Issued" ~ "Performing",
                              dat$loanStatus == "Late (16-30 days)" ~ "Late",
                              dat$loanStatus == "Late (31-120 days)" ~ "Late")

ThreeYear<- as.Date(Sys.time())-(365*3)
FiveYear<- as.Date(Sys.time()-(365*5))

g<- ggplot(dat)
g<- g + aes(x= as.Date(Sys.time())-orderDate, y= CFRatio, group= portfolioName, color= simpleStatus)
g<- g + geom_point()
# g<- g + scale_x_date(limits= c(ThreeYear-150, as.Date(Sys.time())+50))
# g<- g + scale_x_date()
g<- g + facet_wrap(~portfolioName, ncol=2)
g<- g + theme_classic()
g<- g + labs(x= "Age in Days",
             y= "Payback Ratio")
g<- g + geom_hline(yintercept = 100, linetype="dashed")
g<- g + theme(legend.position="none",
              panel.border  = element_rect(colour = "black", fill=NA))
g
```

<hr>
**Principal At Risk** includes outstanding principal of notes greater than 16 days late and notes that have been charged off. 

**Wgt Int Rate** calculation is weighted by the outstanding principal. 

**Payback Ratio** measures the difference between cash invested in a note and the total payments received. The payments include both interest and principal. All notes start at zero and will increase as payments are made.  A note with a ratio greater than 100 indicates that more cash was received than was initially invested.   